POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-10-10 challenges/linearity.tex
dual system streamlined, most sketch of proofs added, but do not trust me

\subsubsection{Semantics}
We describe the actions that the system can perform using a small step operational semantics.
To simplify the definition of the reduction relation, we will  factor out a \emph{structural congruence} relation on processes, namely  ithe smallest congruence relation that satisfies the following axioms:
\begin{mathpar}
  \inferrule[Sc-Par-Comm]{ }{\scong{\Ppar{P}{Q}}{\Ppar{Q}{P}}}
  \and
  \inferrule[Sc-Par-Assoc]{ }{\scong{\Ppar{(\Ppar{P}{Q})}{R}}{\Ppar{P}{(\Ppar{Q}{R})}}}
  \and
  \inferrule[Sc-Par-Inact]{ }{\scong{\Ppar{P}{\Pend}}{P}}
  \and
  \inferrule[Sc-Res-Par]{\{x,y\} \cap \freenames{Q} = \emptyset}{\scong{\Ppar{\Presd{x}{y}{P}}{Q}}{\Presd{x}{y}{(\Ppar{P}{Q})}}}
  \and
  \inferrule[Sc-Res-Inact]{ }{\scong{\Presd{x}{y}{\Pend}}{\Pend}}
  \and
  \inferrule[Sc-Res]{ }{\scong{\Presd{x_1}{y_1}{\Presd{x_2}{y_2}{P}}}{\Presd{x_2}{y_2}{\Presd{x_1}{y_1}{P}}}}
\end{mathpar}

@@

\begin{metanote}
  AM: I've moved the discussion of well-formedness must go after the
  type system, since we want to separate the preservation vs
  safety challemges
\end{metanote}
\paragraph{Syntax}
Our type system does not type processes directly, but instead focuses on the channels used in the process.
The syntax of \emph{session types} \( S, T \) and \emph{type contexts} \( \Gamma \) is as follows:

\begin{align*}
  S,T := &&& \Tend \\
  |&&& \Tbase \\
  |&&& \Tin{S} \\
  |&&& \Tout{S} \\
  \Gamma := &&& \Cempty \\
  |&&& \Cadd{\Gamma}{\hastype{x}{S}}
       %% AM: added
        \\
  |&&& \Cadd{\Gamma}{\hastype{l}{\Tbase}} %% changed, AM
\end{align*}
The \emph{end type}, \( \Tend \), is the type of an endpoint on which no further interaction is possible.
The \emph{base type}, \( \Tbase \), is the type of base values.
The \emph{input type}, \( \Tin{S} \), is the type of an endpoint which is ready to receive a value, then continue with type \( S \).
The \emph{output type}, \( \Tout{S} \), is the type of an endpoint which is ready to send a value, then continue with type \( S \).

@@

\begin{metanote}
  AM: put here the dual rules
\end{metanote}

>>>>

\subsubsection{Semantics}
We describe the actions that the system can perform using a small step operational semantics.
To simplify the definition of the reduction relation, we will  factor out a \emph{structural congruence} relation on processes, namely  the smallest congruence relation that satisfies the following axioms:
\begin{mathpar}
  \inferrule[Sc-Par-Comm]{ }{\scong{\Ppar{P}{Q}}{\Ppar{Q}{P}}}
  \and
  \inferrule[Sc-Par-Assoc]{ }{\scong{\Ppar{(\Ppar{P}{Q})}{R}}{\Ppar{P}{(\Ppar{Q}{R})}}}
  \and
  \inferrule[Sc-Par-Inact]{ }{\scong{\Ppar{P}{\Pend}}{P}}
  \and
  \inferrule[Sc-Res-Par]{\{x,y\} \cap \freenames{Q} = \emptyset}{\scong{\Ppar{\Presd{x}{y}{P}}{Q}}{\Presd{x}{y}{(\Ppar{P}{Q})}}}
  \and
  \inferrule[Sc-Res-Inact]{ }{\scong{\Presd{x}{y}{\Pend}}{\Pend}}
  \and
  \inferrule[Sc-Res]{ }{\scong{\Presd{x_1}{y_1}{\Presd{x_2}{y_2}{P}}}{\Presd{x_2}{y_2}{\Presd{x_1}{y_1}{P}}}}
\end{mathpar}

@@

\begin{metanote}
  AM: I've moved the discussion of well-formedness must go after the
  type system, since we want to separate the preservation vs
  safety challenges
\end{metanote}
\paragraph{Syntax}
Our type system does not type processes directly, but instead focuses on the channels used in the process.
The syntax of \emph{session types} \( S, T \) and \emph{type contexts} \( \Gamma \) is as follows:
\begin{metanote}
  AM: take the syntax from dual file appst.tex and adapt
\end{metanote}
\begin{align*}
  S,T := &&& \Tend \\
  |&&& \Tbase \\
  |&&& \Tin{S} \\
  |&&& \Tout{S} \\
  \Gamma := &&& \Cempty \\
  |&&& \Cadd{\Gamma}{\hastype{x}{S}}
       %% AM: added
        \\
  |&&& \Cadd{\Gamma}{\hastype{l}{\Tbase}} %% changed, AM
\end{align*}
The \emph{end type}, \( \Tend \), is the type of an endpoint on which no further interaction is possible.
The \emph{base type}, \( \Tbase \), is the type of base values.
The \emph{input type}, \( \Tin{S} \), is the type of an endpoint which is ready to receive a value, then continue with type \( S \).
The \emph{output type}, \( \Tout{S} \), is the type of an endpoint which is ready to send a value, then continue with type \( S \).

@@

\begin{metanote}
  AM: put here the dual rules, remove splitting
\end{metanote}
